---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# grasslandbirds

<!-- badges: start -->
<!-- badges: end -->

The goal of grasslandbirds is to provide an analysis and a comparison of the
population of grassland birds in North America, with the production rate of various
livestock and crops. The population data is based on various grassland bird species that
were recorded within the Project Feederwatch survey (2000 - 2024). The production rate,
is taken from the Food and Agriculture Organisation of the United Nations (FAO), the 
data shows the amount of livestock and crops that were produced (in tonnes) in North America. 

## Installation

You can install the development version of grasslandbirds from [GitHub](https://github.com/) with:

``` r
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-rwer0002")
```

## Example

This is a basic example which shows you how to plot the grassland bird population:

```{r example}
library(grasslandbirds)
library(tidyverse)

analysis_data %>%
  ggplot(aes(x = Year, y = population)) +
  geom_line()
```

Moreover, an interactive online app for this data can be deployed by using the
**launch_app** function, within the package. 
